---
title: My dynamic report
output: html_fragment
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)

daily_commute_responses <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vRyT9UZWzU53c1qSzB3qSp6XXQyBvq2GfVeahaK3xWSXtT4drOncOVEvOUK_DJ3v-ax9ZHcD4nRbM2z/pub?gid=19179063&single=true&output=csv"
logged_data <- read_csv(daily_commute_responses)
  
latest_data <- logged_data %>%
  rename(timestamp = 1, 
         transport_mode = 2,  
         weather = 3, 
         commute_rating = 4, 
         traffic = 5, 
         reason = 6, 
         commute_duration = 7)

```

```{css}
body {background-color: seashell; 
     border-style: double;
     border-color: maroon ;
     border-width: 15px}
     
h1 {background-color: seashell;
    font-family: "Cursive";
    text-align: center;
    font-style: italic;
    border-style: double;
    border-color: maroon;
    border-width: 7px;}

h2 {background-color: seashell;
   font-family: "Cursive";
   text-align: center;
   border-style: double;
   border-color: maroon;
   border-width: 7px}

h3 {background-color: seashell;
   font-family: "Cursive";
   text-align: center;
   border-style: double;
   border-color: maroon;
   border-width: 7px}

h4 {background-color: seashell;
   font-family: "Cursive";
   text-align: center;
   border-style: double;
   border-color: maroon;
   border-width: 7px}
   
h1:hover {transform: scale(1.2);
    transition: transform 0.3s ease-in-out;
    box-shadow: 5px 5px 5px 5px purple;}
h2:hover {transform: scale(1.2);
    transition: transform 0.3s ease-in-out;
    box-shadow: 5px 5px 5px 5px purple;}
h3:hover {transform: scale(1.2);
    transition: transform 0.3s ease-in-out;
    box-shadow: 5px 5px 5px 5px purple;}
h4:hover {transform: scale(1.2);
    transition: transform 0.3s ease-in-out;
    box-shadow: 5px 5px 5px 5px purple;}

```
## Analyzing commute duration and satisfaction: Impact of traffic and weather

This dynamic report explores daily commuting patterns of mine collected through a Google Form. It investigates how traffic conditions and weather affect both the duration and satisfaction of my commutes.

The report includes summary statistics and bar charts generated in R, with values dynamically calculated based on the live data. The visualization provide insights into whether external conditions such as traffic or weather influence how I experienced my commutes.

### Commute duration and Traffic

This chart compares commute duration based on traffic presence. I examine whether traffic is associated with longer commute times.

```{r, echo=FALSE}

latest_data %>%
  group_by(traffic) %>%
  summarise(min_duration = min(commute_duration, na.rm = TRUE),
            max_duration = max(commute_duration, na.rm = TRUE))

latest_data %>%
  group_by(traffic) %>%
  summarise(mean_rating = mean(commute_duration, na.rm = TRUE))


#Summary table for dynamic comment
mean_duration_by_traffic <- latest_data %>%
  group_by(traffic) %>%
  summarise(mean_duration = mean(commute_duration, na.rm = TRUE))


#Bar graph 1
latest_data %>%
  ggplot() +
  geom_bar(aes(y = traffic, fill = commute_duration)) +
  labs(title = "Does Commute duration depend on Traffic?",
       subtitle = "Comparing Commute duration with Traffic",
       caption = "Transport mode",
       y = "Traffic (Yes/No)",
       x = "Commute duration")


#Dynamic comment for Bar graph 1
comment1 <- paste("When there was traffic, the average commute duration was", round (mean_duration_by_traffic$mean_duration[mean_duration_by_traffic$traffic == "Yes"], 1),"minutes. Without traffic, it was", round(mean_duration_by_traffic$mean_duration[mean_duration_by_traffic$traffic == "No"], 1)," minutes.")

cat(paste(strwrap(comment1, width = 140), collapse ="\n"))
```

This bar chart compares how many commutes were logged with or without traffic. Commute duration is used as the fill color, which groups bars by duration levels. However, the height of bars reflects count of logs, not average commute time. Observation: More commutes with traffic tend to have longer duration logged.

### Commute rating and Weather

This chart explores whether commute satisfaction (rating) varies depending on the weather conditions.

```{r, echo=FALSE}

latest_data %>%
  group_by(weather) %>%
  summarise(min_duration = min(commute_rating, na.rm = TRUE),
            max_duration = max(commute_rating, na.rm = TRUE))

mean_rating_by_weather <- latest_data %>%
  group_by(weather) %>%
  summarise(mean_rating = mean(commute_rating, na.rm = TRUE))

mean_rating_by_weather

overcast_rating <- mean(
  mean_rating_by_weather$mean_rating[
    mean_rating_by_weather$weather %in% c("Cloudy/foggy", "Windy/cold")])

#Bar graph 2
latest_data %>%
  ggplot() +
  geom_bar(aes(x = weather, fill = commute_rating)) +
  labs(title = "Does Commute rating depend on Weather?",
       subtitle = "Comparing commute rating with Weather",
       caption = "Transport mode",
       x = "Weather",
       y = "Commute rating")  


#Dynamic comment for Bar graph 2
comment2 <- paste("The average commute rating on sunny days was", round(mean_rating_by_weather$mean_rating [mean_rating_by_weather$weather == "Sunny"], 1), "On overcast days with either winds or cold weather, it was", round(overcast_rating, 1))

cat(paste(strwrap(comment2, width = 140), collapse ="\n"))
```

This bar chart shows how certain weather conditions affect commute ratings. Commute rating is used as the fill (not affecting bar height). Observation: Sunny weather had the highest number of positive commute ratings, suggesting that good weather might improve the overall commute experience.
